Score-based tests of measurement invariance: Use in practice

### 2014-04-25 frontiers/frontiers.Rnw
Frontiers paper: Modified code file and added code appendix to ms
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@338 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

All results were obtained using the \proglang{R}~system for statistical computing \cite{R11},
version~\Sexpr{paste(R.Version()[6:7], collapse = ".")}, employing the add-on package
\pkg{lavaan}~\Sexpr{packageDescription("lavaan")["Version"]} \cite{lavaan11} for fitting 
of the factor analysis models and
\pkg{strucchange}~\Sexpr{packageDescription("strucchange")["Version"]} \cite{ZeiLei02,Zei06}
for evaluating the parameter instability tests. \proglang{R}~and both
packages are freely available under the General Public License~2 from the
Comprehensive \proglang{R} Archive Network at \url{http://CRAN.R-project.org/}.
\proglang{R}~code for replication of our results is
available at \url{http://semtools.R-Forge.R-project.org/}.

@@

>>>>

All results were obtained using the \proglang{R}~system for statistical computing \cite{R11},
version~\Sexpr{paste(R.Version()[6:7], collapse = ".")}, employing the add-on package
\pkg{lavaan}~\Sexpr{packageDescription("lavaan")["Version"]} \cite{lavaan11} for fitting 
of the factor analysis models and
\pkg{strucchange}~\Sexpr{packageDescription("strucchange")["Version"]} \cite{ZeiLei02,Zei06}
for evaluating the parameter instability tests. \proglang{R}~and both
packages are freely available under the General Public License~2 from the
Comprehensive \proglang{R} Archive Network at \url{http://CRAN.R-project.org/}.
\proglang{R}~code for replication of our results is
available at \url{http://semtools.R-Forge.R-project.org/} and also in
an online supplement to this article.

@@

\section{Appendix}

The accompanying zip file contains R code for replication of all
analyses and simulations from the article.

\begin{itemize}
  \item mz-frontiers.R: Model estimation functions for simulations.
  \item sim-frontiers.R: Functions for data generation, power
    evaluation, and power summaries.
  \item replication-frontiers.R: Code for the tutorial and
    simulations, utilizing the other two files.
\end{itemize}
